---
title: "My Quarto Doc"
author: Sam Csik
date: 2022-04-14
format:
  html:
    code-fold: true
    code-tools: true
    code-link: true
execute:
  warning: false
  message: false
editor_options: 
  chunk_output_type: console
---

```{r}
#| echo: false

library(tidyverse)
library(palmerpenguins)
```

## Welcome to my quarto doc!

### What is Quarto?

-   quarto is a way of life, a document, a system (lol) that is built for multiple languages (unlike RMarkdown which is a tool developed for R but we've hacked to work with other languages)

-   looks VERY similar to RMarkdown (you're already about 90% of the way there)

### Steps:

1.  open `.qmd` file

2.  switch between source & visual editors

3.  Render (not knit, from `knitr`)

4.  hash pipes `#|` for chunk options

5.  no more global options knitr chunk (all goes in yaml

    execute:

    warning: false

    message: false

6.  author, date in yaml has a more "modern feel"

7.  `#| label: fig-something`, `#| fig-cap: "something"` (use kebab case)

8.  reference figs in-text by their label `@fig-something`

9.  add mpg plot + callout to add axis labels

10. add a tip callout

11. add panel-tabset

12. add second fig to first chunk with updated chunk options `fig-subcap:`, `layout-ncol: 2`, and `column: page`

::: callout-note
## This plot still needs updated axis labels!

```{r}
#| label: fig-mpg
#| fig-cap: "This is my mpg figure"
#| fig-subcap: 
#|  - "Color by number of cylinders"
#|  - "Color by engine displacement, in liters"
#| fig-alt: "Here is my very descriptive alt text for this first figure"
#| layout-ncol: 2
#| column: page

ggplot(mpg, aes(x = hwy, y = cty, color = cyl)) +
  geom_point(alpha = 0.5) +
  scale_color_viridis_c() +
  theme_minimal()

ggplot(mpg, aes(x = hwy, y = cty, color = displ)) +
  geom_point(alpha = 0.5) +
  scale_color_viridis_c() +
  theme_minimal()
```
:::

@fig-mpg is my first ever cross-referenced quarto figure and I'm very excited about it. @fig-mpg-1 is colored by number of cylinders and @fig-mpg-2 is colored by engine displacement.

::: callout-tip
Reminder! In Visual editor mode, you can add callouts under the Insert drop down menu.
:::

## Surprise! Tabsets!

::: panel-tabset
## my first tab

hello, it's me

## my second tab

surprise, there's more content here!
:::
